---
title: "Assignment"
author: "Scott Stoltzman"
date: "6/12/2019"
output: html_document
---

Display all of your answers by simply writing the variable name at the end of the code block.

Load libraries that you need
```{r setup, warning=FALSE, message=FALSE}
library("tidyverse")
library("DBI")
```

Connect to `chinook.db`
```{r}
con <-DBI::dbConnect(RSQLite::SQLite(), "chinook.db")
```


Create variables to represent the tables: `genres, albums, artists, tracks, invoices, customers, media_types`. This will make it easier to use these tables later on.
```{r}
genres = tbl(con, 'genres')
albums = tbl(con, 'albums')
artists = tbl(con, 'artists')
tracks = tbl(con, 'tracks')
invoices = tbl(con, 'invoices')
customers = tbl(con, 'customers')
media_types = tbl(con, 'media_types')
```


Who are the first 10 `customers` in the database? Return only `FirstName` and `LastName`
Answer using SQL and `dbGetQuery()` (not `tbl()`)
```{r}
qry = 'SELECT FirstName, LastName FROM customers LIMIT 10'
dbGetQuery(con, qry)

```


Complete the same task as above using `tbl()`
```{r}

tbl(con, 'customers') %>%
  select(FirstName, LastName) %>%
  head(10)

```


For the rest of the assignment, use the `tbl()` ... you may use raw SQL if it is easier for you.


Count the number of `customers` by `country` and arrange in descending order.
```{r}
customers %>%
  group_by(Country) %>%
  summarize(n = n())%>%
  arrange(desc(n))

  
```


```{r}
invoices
```


Plot the sum of `Total` from invoices by year in a line chart.
```{r}
invoiceplot <- invoices %>%
  mutate(year = substr(InvoiceDate, 1, 4)) %>%
  group_by(year) %>%
  summarise(yeartotal=sum(Total))

invoiceplot


```


```{r}
  ggplot(invoiceplot, mapping = aes(x=year, y= yeartotal)) +
    geom_point()+
    geom_line()
```



```{r}

albums

```

```{r}
genres = tbl(con, 'genres') %>% as_data_frame()
albums = tbl(con, 'albums') %>% as_data_frame()
artists = tbl(con, 'artists') %>% as_data_frame()
tracks = tbl(con, 'tracks') %>% as_data_frame()
invoices = tbl(con, 'invoices') %>% as_data_frame()
customers = tbl(con, 'customers') %>% as_data_frame()
media_types = tbl(con, 'media_types') %>% as_data_frame()
invoice_items = tbl(con, 'invoice_items') %>% as_data_frame()


```


```{r}

```



What's the average length of a `track` for each `artist` on each `album`?
```{r}


trackdata <- tracks %>%
 select(TrackName = Name, AlbumId, Milliseconds, Bytes, UnitPrice)

trackdata <-
  left_join(trackdata, albums, by = c("AlbumId" = "AlbumId")) %>%
  select(TrackName, AlbumTitle = Title, ArtistId, Milliseconds, Bytes, UnitPrice)

trackdata <-
  left_join(trackdata, artists, by = c("ArtistId" = "ArtistId")) %>%
  select(TrackName, AlbumTitle, ArtistName = Name, Milliseconds, Bytes, UnitPrice) %>%
  mutate(ArtistAlbum = paste(ArtistName, AlbumTitle)) %>%
  arrange(desc(ArtistAlbum))

trackdata


```

```{r}
trackmean <- trackdata %>%
  group_by(ArtistAlbum) %>%                          
  summarise(mean_mil = mean(Milliseconds))

trackmean
```




If the different `media_types` cost different amounts of money to sell, calculate your top 10 most profitable tracks. For this example, all costs are equal EXCEPT for the `media_type`.  

COSTS:  

  - MPEG = $0.15
  - Protected MPEG-4 = $0.25
  - AAC = $0.03
  - Protected AAC = $0.10
  - Purchased AAC = $0.08
  
```{r}
media_types <- media_types %>%
  mutate(cost= c(.15, .10, .25, .08, .03))
media_types
invoice_items
```
  
  
```{r}
incomedata <- invoice_items %>%
  select(TrackId, Quantity)


incomedata <-    left_join(incomedata, tracks, by = c("TrackId" = "TrackId")) %>%
select(TrackId, UnitPrice, Quantity, TrackName = Name, MediaTypeId, Milliseconds, Bytes, UnitPrice)


trackincome <-    left_join(incomedata, media_types, by = c("MediaTypeId" = "MediaTypeId")) %>%
select(TrackId, UnitPrice, Quantity, TrackName, MediaTypeId, Milliseconds, Bytes, UnitPrice, cost) %>%
  mutate(income = UnitPrice - cost) %>%
  group_by(TrackId) %>%
  summarise(tot_income = sum(income)) %>%
  arrange(desc(tot_income))

incomedata <- left_join(incomedata, trackincome, by = c("TrackId" = "TrackId")) %>%
  arrange(desc(tot_income)) %>%
  top_n(10)

incomedata



```


Create a Scatter Plot of `tracks`, x = milliseconds and y = bytes 
```{r}
tracks %>%
  ggplot(aes(x = Milliseconds, y = Bytes))+
  geom_jitter()
```


Create a Scatter Plot of `tracks`, x = milliseconds and y = bytes, `facet_wrap` by `media_type`
```{r}
tracks %>%
  ggplot(aes(x = Milliseconds, y = Bytes))+
  geom_jitter()+
  facet_wrap(~MediaTypeId)
```


Create a linear regression model using `milliseconds` as a predictor of `bytes`. Hint, formula: `bytes ~ milliseconds`
```{r}
  model_1 = lm(Bytes ~ Milliseconds, data=trackdata)
summary(model_1)
```


Create a linear model using the same formula but split it out according to `media_type`
```{r}
model_2 = lm(Bytes ~ MediaTypeId, data=tracks)
summary(model_2)
```


Create a linear model using the same formula but split it out according to `artist`

## I JUST POOPED OUT.  I know that I need to do a left join with tracks to albums to artists.  But I don't know if 


```{r}
model_3 = lm(Bytes ~ ArtistName, data=trackdata)
summary(model_3)
```

