---
title: "Assignment"
author: "Scott Stoltzman"
date: "6/12/2019"
output: html_document
---

Display all of your answers by simply writing the variable name at the end of the code block.

Load libraries that you need
```{r setup, warning=FALSE, message=FALSE}
library("tidyverse")
library("DBI")
```

Connect to `chinook.db`
```{r}
chasecon <-DBI::dbConnect(RSQLite::SQLite(), "chinook.db")
```


Create variables to represent the tables: `genres, albums, artists, tracks, invoices, customers, media_types`. This will make it easier to use these tables later on.
```{r}
genres = tbl(con, 'genres')
albums = tbl(con, 'albums')
artists = tbl(con, 'artists')
tracks = tbl(con, 'tracks')
invoices = tbl(con, 'invoices')
customers = tbl(con, 'customers')
media_types = tbl(con, 'media_types')
```


Who are the first 10 `customers` in the database? Return only `FirstName` and `LastName`
Answer using SQL and `dbGetQuery()` (not `tbl()`)
```{r}
qry = 'SELECT FirstName, LastName FROM customers LIMIT 10'
dbGetQuery(con, qry)

```


Complete the same task as above using `tbl()`
```{r}
customers %>%
  filter(CustomerId <=10) %>%
  select(FirstName, LastName)
```


For the rest of the assignment, use the `tbl()` ... you may use raw SQL if it is easier for you.


Count the number of `customers` by `country` and arrange in descending order.
```{r}
customers %>%
  group_by(Country) %>%
  summarize(n = n())%>%
  arrange(desc(n))

  
```


```{r}
invoices
```


Plot the sum of `Total` from invoices by year in a line chart.
```{r}
invoiceplot <-invoices %>%
  mutate(year = substr(InvoiceDate, 1, 4)) %>%
  group_by(year) %>%
  geom_line()

```

```{r}


```


What's the average length of a `track` for each `artist` on each `album`?
```{r}
invoices
```



If the different `media_types` cost different amounts of money to sell, calculate your top 10 most profitable tracks. For this example, all costs are equal EXCEPT for the `media_type`.  

COSTS:  

  - MPEG = $0.15
  - Protected MPEG-4 = $0.25
  - AAC = $0.03
  - Protected AAC = $0.10
  - Purchased AAC = $0.08
  
```{r}
#
```


Create a Scatter Plot of `tracks`, x = milliseconds and y = bytes 
```{r}

```


Create a Scatter Plot of `tracks`, x = milliseconds and y = bytes, `facet_wrap` by `media_type`
```{r}

```


Create a linear regression model using `milliseconds` as a predictor of `bytes`. Hint, formula: `bytes ~ milliseconds`
```{r}

```


Create a linear model using the same formula but split it out according to `media_type`
```{r}

```


Create a linear model using the same formula but split it out according to `artist`
```{r}

```

